Leader functions and qualities across 59 cultures: an exploratory analysis

### 2019-11-26 leadership_across_cultures_contexts.Rmd
Moved sections around
Latest stuff

---
title: "Leader functions and qualities across 59 cultures: an exploratory analysis"
author: "Zachary J. Garfield, Kristen L. Syme, and Edward H. Hagen"
date: "4/25/2019"
output: 
  bookdown::html_document2
bibliography: Leader2.bib
---

@@

@@

>>>>

---
title: "Leader functions and qualities across 59 cultures: an exploratory analysis"
author: "Zachary H. Garfield, Kristen L. Syme, and Edward H. Hagen"
date: "4/25/2019"
output: 
  bookdown::html_document2
bibliography: Leader2.bib
---

@@

## Distribution of text records by group type and sex

The type of group to which a leader text referred was coded into seven categories. Figure \@ref(fig:groupsex) indicates the proportion of text records that were categorized into each of these groups; it also indicates the proportion of male and female leaders of each type of group.

```{r groupsex, fig.width=15, fig.cap="The distribution of text records by group type and leader sex. Areas of the bars are proportional to the number of text records in that category. There were no female leaders in any military or religious group."}
plot_group_sex
```

@@

## Benefits and costs of leadership and followership
